Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-12 vesicle_code/docs/adhesion/adhesion.tex
went through extensional again

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
point (zero-velocity at the origin) in an extensional flow, $\uu =\chi(-x,y)$,
is a saddle point where two laminar streams converge along an axis and
then diverge in the orthogonal direction.  With an active control algorithm
to place the stagnation point at a desirable location by adjusting the streaming
flow strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
particle can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as particle
image velocimetry of flow inside and around the particle.  To explore
the application of such a fluid trap to measure the adhesion strength
between two bound vesicle membranes, we propose the following thought
experiment.  Beginning with two identical vesicles in an equilibrium
configuration that form a doublet with a flat contact region
(Figure~\ref{fig:Dec18_vesicle_shape}), we turn on the fluid trap with
the stagnation point placed at the center of the vesicle doublet.
Depending on the Hamaker constant, we expect that either the flow
overcomes the adhesive force and the doublet is broken, or the adhesive
force dominates and the doublet reaches a stable stationary
configuration.

\begin{figure}[htp]
    \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
    \hspace{20pt}
    \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
    \hspace{20pt}
    \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
   \caption{\label{fig:InclinationAngle} The definition of the
   inclination angle of a vesicle doublet at the center of an
   extensional flow.  An inclination angle of $\pi$ indicates a doublet
   whose long axis is parallel to the diverging direction, while an
   inclination angle of $\pi/2$ indicates a doublet whose short axis is
   parallel to the diverging direction.  The square mark is a stagnation
   point and the round point is located at the center of the vesicle.
   The initial configurations in this section all have an initial
   configuration of $\theta = \pi$.}
   \end{figure}

@@

Based on how the contact region aligns with the extensional flow, we can
define the inclination angle of the vesicle doublet as illustrated in
Figure~\ref{fig:InclinationAngle}. When $\theta=\pi$ (the doublet long
axis is aligned with the far-field converging flow), the diverging flow
pulls the vesicles apart from each other and the short-range repulsive
force is essential to keep the two vesicles from separating.  In
contrast, when $\theta = \pi/2$ (the doublet long axis is aligned with
the diverging flow), the converging flow pushes the vesicles towards
each other and the short-range repulsive force is essential to keep the
two vesicles at the separation distance.  With the converging flow
pushing the two vesicles towards the stagnation point dynamically placed
at the doublet center, this configuration is expected to be more stable
than the $\theta=\pi$ configuration in the left of
Figure~\ref{fig:InclinationAngle}, where the doublet long axis is
parallel to the converging direction. This is because when $\theta=\pi$
the diverging flow is pulling the vesicles away from each other as shown
in the illustration.  If the doublet inclination angle is fixed at
$\theta=\pi/2$, the vesicle doublet stays intact only when the adhesive
force is strong enough to dominate over the fluid drag in this
configuration \todo[inline]{I don't follow this sentence}.  Thus it is
possible that the diverging flow may overcome adhesion and break up the
doublet. It is also reasonable to expect a vesicle doublet to rotate
from $\theta=\pi$ to $\theta=\pi/2$, such that the fluid flow is pushing
them together rather than pulling them apart.

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
point can be controlled in an experimental
setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control of
the microfluidic experiments by moving the center of the doublet at each
time step so that the stagnation point occurs exactly in the middle of
the doublet.  With this adjustment, the vesicles either remain as a
doublet in the fluid trap centered around the stagnation point, or the
doublet is broken and the vesicles separate from one another.  In
Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
different extensional rates.  While this doublet remains bound for all
the considered extensional rates, a doublet with a reduced area of
$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =0.1$
(Figure~\ref{fig:extensional3}).  For extensional rates and reduced
areas that result in a bound vesicle doublet, we observe that the
doublet always rotates from $\theta=\pi$ configuration towards the more
stable $\theta=\pi/2$ configuration, as shown in
Figures~\ref{fig:extensional1}.  We also observe that in most cases with
moderate extensional flow rates the doublet falls short of aligning
their long axis with the diverging direction.

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced
  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
  the separation distance is $\delta = 0.4$, and the extensional rate is
  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
  square, is a stagnation point.}
  \end{figure}

 \begin{figure}
    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced area
  $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The
  Hamaker constant $\mathcal{H} = 0.7$, the adhesion length scale
  $\delta = 0.4$, and the extensional rate $\chi = 0.1$.  The center of
  the vesicle, denoted with a black square, is a stagnation point.}
  \end{figure}

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (middle).  We observe that not
only do larger smaller extensional rates result in smaller inclination
angles, but smaller reduced areas also result in smaller inclination
angles.  Moreover, the critical Hamaker constant that determines if the
doublet remains trapped or is broken decreases with an increasing
extensional rate.  We summarize the final inclination angle of the
doublet in the right plot of
Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
dots are scaled to the final inclination angle as defined in
Figure~\ref{fig:InclinationAngle}.  At smaller extensional rates, the
vesicles come closer to aligning their long axis with the diverging
direction.  When the doublet is broken at reduced area $\Delta A =
0.80$, the extensional rate is sufficiently large to align the long axis
of the vesicle with the diverging direction and then the vesicles
separate (Figure~\ref{fig:extensional3}).  For very low extensional
rates, the time horizon is insufficient for the doublet to reach an
equilibrium state, and these simulations are marked with a square.  The
right plot of Figure~\ref{fig:extensionalInclinationAngle} also
summarizes the reduced areas and extensional rates that result in a
bound vesicle doublet in a fluid trap: Parameter values with a blue mark
result in a fluid trap and parameter values with a red mark result in
vesicle separation.

\begin{figure}[htp]
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $\Delta A = 0.7$ submerged in an extensional flow with an extensional
  rate of $\chi$.  {\em Middle}: The final inclination angle of
  doublets.  At larger extensional rates, the doublet is broken by the
  flow.  {\em Right}: A phase diagram of the long-time behavior of a
  fluid trap formed by two adhering vesicles in an extensional flow.
  Results are not reported for some of the low extensional rates since
  the doublet had not tilted to an equilibrium inclination angle for the
  given time horizon.}
\end{figure}

Finally, to further characterize the rotating dynamics of a doublet in
the fluid trap, we compute and plot the vorticity and total force on a
doublet with identical vesicles with reduced area $\Delta A=0.7$,
separation distance $\delta = 0.4$, Hamaker constant $\mathcal{H} =
0.7$, and extensional rate $\chi = 0.7$ in
Figure~\ref{fig:extensionalVorticity}.  Starting from a vesicle doublet
with an initial inclination angle $\theta=\pi$, the doublet slowly
begins to rotate around $t\sim 265$.  We notice that the net force on
each vesicle is almost anti-parallel to the diverging flow in the
far-field so to balance the hydrodynamic drag force that pulls the
vesicles apart.  Then, as the doublet starts to rotate, each vesicle
experiences a drag force from both up and down diverging streaming flows.
For small extensional rate, the rotation will continue until $\theta =
\pi/2$ so the doublet remains perfectly symmetric with respect to their
mid-plane  and each vesicle experiences drag forces that cancel in both
directions.  For slightly higher extensional rate, we observe that the
two vesicles slide against each other as the doublet rotates.  The slight
sliding motion leads to a transition in the contact region membrane
shape from a bulging profile to an S-shape profile of nearly uniform
height except near the edge of contact region.  This adjustment greatly
reduces the net force on each vesicle, leading to an equilibrium
configuration with an inclination angle $\theta > \pi/2$ as shown in the
left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the
vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A =
  0.7$, the extensional rate is $\chi = 0.7$, the separation distance is
  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
point (zero-velocity at the origin) in an extensional flow, $\uu
=\chi(-x,y)$, is a saddle point where two laminar streams converge along
an axis and then diverge in the orthogonal direction.  With an active
control algorithm to place the stagnation point at a desirable location
by adjusting the streaming flow strength with a feedback
loop~\cite{Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
stagnation point for long time scales to facilitate image acquisition or
other detailed measures such as particle image velocimetry of flow
inside and around the particle.  To explore the application of such a
fluid trap to measure the adhesion strength between two bound vesicle
membranes, we propose the following thought experiment.  Beginning with
two identical vesicles in an equilibrium configuration that form a
doublet with a flat contact region
(Figure~\ref{fig:Dec18_vesicle_shape}), we turn on the fluid trap with
the stagnation point placed at the center of the vesicle doublet.
Depending on the Hamaker constant, we expect that either the flow
overcomes the adhesive force and the doublet is broken, or the adhesive
force is sufficiently strong and the doublet reaches a stable stationary
configuration.

@@

\begin{figure}[htp]
   \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
   \hspace{20pt}
   \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
   \hspace{20pt}
   \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
   \caption{\label{fig:InclinationAngle} The definition of the
   inclination angle of a vesicle doublet at the center of an
   extensional flow.  An inclination angle of $\pi$ indicates a doublet
   whose long axis is orthogonal to the diverging direction, while an
   inclination angle of $\pi/2$ indicates a doublet whose short axis is
   orthogonal to the diverging direction.  The square mark is a
   stagnation point and the round point is located at the center of the
   vesicle.  The initial configurations in this section all have an
   inclination angle of $\theta = \pi$.}
 \end{figure}

Based on how the contact region aligns with the extensional flow, we can
define the inclination angle of the vesicle doublet as illustrated in
Figure~\ref{fig:InclinationAngle}. When $\theta=\pi$, the doublet long
axis is aligned with the far-field converging flow, and the diverging flow
pulls the vesicles apart from each other and the long-range attractive
force is essential to keep the two vesicles from separating.  In
contrast, when $\theta = \pi/2$, the doublet long axis is aligned with
the diverging flow, the converging flow pushes the vesicles towards
each other and the short-range repulsive force is essential to keep the
two vesicles at the separation distance.  With the converging flow
pushing the two vesicles towards the stagnation point dynamically placed
at the doublet center, this configuration is expected to be more stable
than the $\theta=\pi$ configuration in the left of
Figure~\ref{fig:InclinationAngle}. This is because when $\theta=\pi$ the
diverging flow is pulling the vesicles away from each other as shown in
the illustration.  However, when the doublet inclination angle is fixed
at $\theta=\pi/2$, the vesicle doublet stays intact if the adhesive
force is strong enough to dominate the fluid drag.  However, it is
possible that the diverging flow may overcome adhesion and break up the
doublet.  It is also reasonable to expect a vesicle doublet to rotate
from the less stable configuration $\theta=\pi$ to the more stable
configuration $\theta=\pi/2$, so that the fluid flow is pushing them
together rather than pulling them apart.

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
point can be controlled in an experimental
setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control of
the microfluidic experiments by moving the center of the doublet at each
time step so that the stagnation point occurs exactly in the middle of
the doublet.  With this adjustment, the vesicles either remain as a
doublet in the fluid trap centered around the stagnation point, or the
doublet is broken and the vesicles separate from one another.  In
Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing a
vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at three
different extensional rates.  We observe that the doublet rotates from
$\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
configuration, as shown in Figures~\ref{fig:extensional1}.  We also
observe that with moderate extensional rates, the doublet falls short of
aligning their long axis with the diverging direction.  Moreover, the
final inclination angle is closest to the stable $\theta=\pi/2$ for the
smallest extensional rates.  While this doublet remains bound for all
the considered extensional rates, a doublet with a reduced area of
$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =
0.1$ (Figure~\ref{fig:extensional3}).

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced
  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
  the separation distance is $\delta = 0.4$, and the extensional rate is
  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
  square, is the stagnation point.}
  \end{figure}

 \begin{figure}
    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi$.  The reduced area
  is $\Delta A = 0.8$, the Hamaker constant $\mathcal{H} = 0.7$, the
  separation distance is $\delta = 0.4$, and the extensional rate $\chi
  = 0.1$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (middle).  We observe that not
only do smaller extensional rates result in smaller inclination
angles, but smaller reduced areas also result in smaller inclination
angles.  Moreover, the critical Hamaker constant that determines if the
doublet remains trapped or is broken decreases with an increasing
extensional rate \todo[inline]{not sure how we can say this since we've
only considered one Hamaker constant}.  We summarize the final
inclination angle of the doublet in the right plot of
Figure~\ref{fig:extensionalInclinationAngle}.  The size of the round
dots are scaled to the final inclination angle as defined in
Figure~\ref{fig:InclinationAngle}.  At smaller extensional rates, the
vesicles come closer to aligning their long axis with the diverging
direction.  When the doublet is broken at reduced area $\Delta A =
0.80$, the extensional rate is sufficiently large to align the long axis
of the vesicle with the diverging direction and then the vesicles
separate (Figure~\ref{fig:extensional3}).  For very low extensional
rates, the time horizon is insufficient for the doublet to reach an
equilibrium state, and these simulations are marked with a square.  The
right plot of Figure~\ref{fig:extensionalInclinationAngle} also
summarizes the reduced areas and extensional rates that result in a
bound vesicle doublet in a fluid trap: Parameter values with a blue mark
result in a fluid trap and parameter values with a red mark result in
vesicle separation.

\begin{figure}[htp]
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $\Delta A = 0.7$ in an extensional flow with an extensional rate
  $\chi$.  {\em Middle}: The final inclination angle of doublets.  At
  larger extensional rates, the doublet is broken by the flow.  {\em
  Right}: A phase diagram of the long-time behavior of a fluid trap
  formed by two adhering vesicles in an extensional flow.  Results are
  not reported for some of the low extensional rates since the doublet
  had not tilted to an equilibrium inclination angle for the given time
  horizon.}
\end{figure}

Finally, to further characterize the rotating dynamics of a doublet in
the fluid trap, we compute and plot the vorticity and total force on a
doublet with identical vesicles with reduced area $\Delta A=0.7$,
Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
0.4$, and extensional rate $\chi = 0.7$ in
Figure~\ref{fig:extensionalVorticity}.  Starting from a vesicle doublet
with an initial inclination angle $\theta=\pi$, the doublet slowly
begins to rotate around $t\sim 250$.  We notice that the net force on
each vesicle is almost anti-parallel to the diverging flow in the
far-field so to balance the hydrodynamic drag force that pulls the
vesicles apart.  Then, as the doublet starts to rotate, each vesicle
experiences a drag force from both the up and down diverging streaming
flows.  For small extensional rate, the rotation will continue until
$\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
to their mid-plane and each vesicle experiences drag forces that cancel
in both directions.  For slightly higher extensional rate, we observe
that the two vesicles slide against each other as the doublet rotates.
The slight sliding motion leads to a transition in the contact region
membrane shape from a bulging profile to an S-shape profile of nearly
uniform height except near the edge of contact region.  This adjustment
greatly reduces the net force on each vesicle, leading to an equilibrium
configuration with an inclination angle $\theta > \pi/2$ as shown in the
left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the
vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A =
  0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.7$.}
\end{figure}
